Proposal

### 2022-06-10 proposal/CopyOfproposal.qmd
started editing the proposal

<!-- -->

-   WVS post-materialist index (-1 = materialist. 2 = mixed. 3 =
    post-materialist)

@@

@@

```{r eda-year}
#| warning: false
#Year of survey
ggplot(abortion_data, aes(x = year)) +
  geom_histogram() + 
  labs(title = "Histogram of year")
ggplot(abortion_data, aes(x = year, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r eda-age}
#| warning: false
#Age
ggplot(abortion_data, aes(x = age)) +
  geom_histogram(binwidth = 1) + 
  labs(title = "Histogram of age")
ggplot(abortion_data, aes(x = age, y = aj)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

@@

@@

The data dictionary can be found
[here](https://github.com/STA210-Summer22/project-bayes-harem/blob/main/data/README.md).

>>>>

```{=html}
<!-- -->
```
-   WVS post-materialist index (-1 = materialist. 2 = mixed. 3 =
    post-materialist)

@@

We can observe from this histogram that the distribution of the outcome variable is not a bell shape, and it is trimodal. This is likely because the question's phrasing is similar to a yes/no question, but respondents were asked to give their level of agreement on a scale of 1-10. This may result in our model not being a good fit for the data if we attempt a multiple linear regression model. We have two backup plans for this, if our MLR eventually has a poor performance. First, we can truncate this data into a categorical outcome variable such as (Agree, Disagree, Undecided), and conduct a binomial or multinomial logistic regression. Second, we can filter our population based on various characteristics (if we have good reason to do so) so that our outcome data follows a bell shape.

@@

```{r eda-year}
#| warning: false
#Year of survey
ggplot(abortion_data, aes(x = year)) +
  geom_histogram() + 
  labs(title = "Histogram of year")
ggplot(abortion_data, aes(group = year, y = aj)) +
  geom_boxplot() 
```

```{r eda-age}
#| warning: false
#Age
ggplot(abortion_data, aes(x = age)) +
  geom_histogram(binwidth = 1) + 
  labs(title = "Histogram of age")
#ggplot(abortion_data, aes(group = age, y = aj)) +
  #geom_density() try to group together
```

@@

 Is there a plan B ? how to deal ? MLR compare

@@

The data dictionary can be found [here](ADD%20LINK!!!).
